Fig3

### 2020-05-12 analysis/figure-3.Rmd
fig 3 working

PRLpit <- candidatevsd %>% filter(tissue == "pituitary", gene == "PRL") %>%
  mutate(hiloPRL = ifelse(counts >= 18, "hi", "lo"))  %>%
  drop_na()
PRLpit$hiloPRL <- factor(PRLpit$hiloPRL, levels = c("lo", "hi"))

>>>>

PRLpit <- candidatevsd %>% 
  filter(tissue == "pituitary", 
         gene == "PRL",
         treatment %in% charlevels) %>%
  mutate(treatment = factor(treatment, levels = charlevels))  %>%
  mutate(hiloPRL = ifelse(counts >= 18, "hi", "lo"))  %>%
  drop_na()
PRLpit$hiloPRL <- factor(PRLpit$hiloPRL, levels = c("lo", "hi"))
